Syntax and Semantics of Abstract Binding Trees

### 2015-12-12 paper.tex
add remark about a general thy of behavioral refinements

>>>>

\begin{remark}
  In the full development of a theory of behavioral refinements, the ad-hoc
  judgment $\IsWf{\Upsilon}{\Gamma}{M}{\tau}$ would be replaced with a general
  notion of refinement $\IMode{\phi}\sqsubset\tau$ ($\phi$ refines sort
  $\tau$), and a new judgment $\IMode{\Upsilon}\parallel\IMode{\Phi}\vDash
  \IMode{M} \in \IMode{\phi}$, such that $\phi$ refines $\tau$ the
  refinement context $\Phi$ refines some sort context $\Gamma$. Furthermore, in
  addition to restricting membership, refinements might also be designed to
  coarsen equivalence.
\end{remark}
